---
title: "Exercise #3"
subtitle: "Fortgeschrittene Statistische Software für NF - SS 2022/23"
author: "Marius Jacobs (12573264), Niels Glodny (12568548), ..."
date: "`r Sys.Date()`"
---

## Exercise 1: Initializing git (4 Points)

d)  Strengths: 
    - Git is a distributed version control system, meaning that each user can have a complete local copy of the project. The users are able to work together 
    without strictly needing a central entity for the project, even if it can 
    be used to improve the experience.
    - Git has a big community and is well supported by many tools. For example, 
    most IDEs like R-Studio have integrated Git into their UI. There are also a 
    lot of websites providing hosting for your git project
    
    Weaknesses: 
    - It's not the most intuitive system. The command line interface is a bit 
    convoluted and has many commands that can become complex. As a result, it has a steep learning curve. 
    - Git is not well-suited to track versions of big files or files that are not in
    a plain-text format. For example, it will not be able to track the changes in
    an image and instead store the entire image for each new version.

## Exercise 2: Putting your Repository on GitHub (3.5 Points)

For this task you will upload your solution to GitHub.

a)  Create a new repository on GitHub in your account named
    `exeRcise-sheet-3`. Make sure you create a **public repository** so
    we are able to see it for grading. Add the link to the repository
    below: https://github.com/yndolg/exeRcise-sheets-3
b)  
```{}
    git remote add origin git@github.com:yndolg/exeRcise-sheets-3.git
    git branch -M main
    git push -u origin main
```
c)  Regularly push your latest changes to GitHub again and especially do
    so when you are finished with this sheet.

## Exercise 3: Baby-Names in Munich (4.5 Points)

Download the latest open datasets on given names ("Vornamen") from the
open data repository of the city of Munich for the years `2022` and
`2021`.

Link: <https://opendata.muenchen.de/dataset/vornamen-von-neugeborenen>

a)  Download the data for both years and track it in git. For small
    datasets like these adding them to git is not a problem.

b) The problem is that for counts lower or equal to 4, the data set only contains
    "4 oder weniger". To solve this issue, we've set all of these values to 2,
    as this might roughly preserve the total number of babies. This is an
    estimate for the average count over these values. Of course, they are likely
    not uniformly distributed, but we don't have much information to take a 
    more informed guess.

```{r}
    library(readr)
    library(dplyr)
    data22 <- read_csv("vornamen_2022.csv")
    data21 <- read_csv("vornamen_2021.csv")
    data22 <- data22 %>% mutate(AnzahlNum = parse_number(ifelse(Anzahl == "4 oder weniger", "2", Anzahl)))
    data21 <- data21 %>% mutate(AnzahlNum = parse_number(ifelse(Anzahl == "4 oder weniger", "2", Anzahl)))
```

c)  More babys were born in 2021.
```{r}
    sum22 <- sum(data22$AnzahlNum)
    sum21 <- sum(data21$AnzahlNum)
    print(paste("There were", sum21, "babys born in 2021 and", sum22, "babys born in 2022."))
```
  
d)  
```{r}
  data22 <- data22 %>% mutate(year = 2022)
  data21 <- data21 %>% mutate(year = 2021)
```
    

e)  Combine both datasets into one using `bind_rows()`.

f)  Combine the counts for same names to determine the most popular
    names across both years. Print out the top 10 names in a nicely
    formatted table for both years. Include a table caption.

## Exercise 4: Chat GPT + apply (3 points)

For this task: Specifically use ChatGPT to solve the task and submit
your prompts in addition to the solution

a)  The code below does not work because the wrong apply function has
    been used. Find out which apply function would be correct and why it
    did not work. Correct the code. Also calculate the rowwise means.

###Create a sample data frame

tax_data \<- data.frame( Name = c("Munich GmbH", "ABC Inc.", "Backpacks
1980", "Bavarian Circus"), Tax_2019 = c(5000, 4000, 6000, 3500),
Tax_2020 = c(4800, 4200, 5800, 3700), Tax_2021 = c(5200, 3800, 5900,
3400) )

###Calculate column-wise means

column_means \<- lapply(tax_data\[, -1\], 2, mean)

column_means

b)  Using ChatGPT try to understand what the rapply() function does.
    Create an easy example with mock data where the function is used and
    explain it in your words.

## Final Note

Make sure to push all your commits and changes to GitHub before
submittining the exercise sheet.
